Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-15 numerical-starformation.tex
Adding ray tracing method section (a little more than a page).  Fixed a lot of missing references and citations.
working on star formation section, 1st checkin.

%\red{By the time this paper is submitted my (BWO's) paper on the star formation
%and feedback algorithms, and the various parameters contained therein, should be
%at least written and submitted as well.  Point to this, and maybe include a couple
%interesting plots (perhaps in an appendix?).}
%GB: can we really point to that paper?

While the physics discussed previously is all crucial to the study of
cosmological structure formation, most cosmological observations are of
stars and related phenomena.  Additionally, stars eject energy and metal-
enriched gas throughout their lives, drastically modifying their own 
environment.  The formation of galaxies and clusters cannot be completely
modeled without including the feedback of energy and metals.  In particular,
it is thought that feedback is crucial for suppressing the large numbers of
dwarf-like galaxies that CDM theories predict 
\citep{1991ApJ...381...14L,1991ApJ...379...52W}.  An early
burst of star formation could remove a large fraction of cold gas from such systems
\citep{1978MNRAS.183..341W,1991ApJ...367...45C}.  Also, the unexpectedly 
low luminosities of small clusters and
groups (relative to the richest clusters) is commonly explained through feedback
\citep{1991ApJ...383..104K}.  Energy ejected during the formation of the cluster ellipticals 
lowers the central density and hence the X-ray luminosity of such clusters 
 \citep{1997ApJ...484L..21C}.  Therefore, the inclusion of star formation and the 
feedback of energy and metals into the intergalactic medium in a cosmological
code is crucial for many reasons.

>>>>

While the physics discussed in other sections of this paper is crucial to the study of
cosmological structure formation, most cosmological observations in
the infrared, optical, and ultraviolet wavelengths are of
stellar populations.  Furthermore, stars eject energy and metal-
enriched gas throughout their lives, drastically modifying their own 
environments' cooling properties.  Broadly speaking, the formation of galaxies and clusters cannot be completely
modeled without including the feedback of energy and metals.  In particular,
it is thought that feedback is crucial for suppressing the large numbers of
dwarf-like galaxies that CDM theories predict 
\citep{1991ApJ...381...14L,1991ApJ...379...52W}.  An early
burst of star formation could remove a large fraction of cold gas from such systems
\citep{1978MNRAS.183..341W,1991ApJ...367...45C}.  Also, the unexpectedly 
low luminosities of small clusters and
groups (relative to the richest clusters) is commonly explained through feedback
\citep{1991ApJ...383..104K}.  Energy ejected during the formation of the cluster ellipticals 
lowers the central density and hence the X-ray luminosity of such clusters 
 \citep{1997ApJ...484L..21C}.  For all of these reasons, it is
 critical to include star formation and the feedback of energy and
 metals into the interstellar and intergalactic media in cosmological simulations.
